%\vspace{-0.05in}
\section{Conclusion}
\label{conclus}
The major contribution of this paper is to develop $Q_M$, a novel modularity index for evaluating the quality of communities in 
multilayer networks.
It is experimentally shown that this index overcomes the limitations of the state of the art multilayer modularity
definitions~\cite{CompMod,medical_paper} and behaves as per expectation in the various topological scenarios.
% That is why unlike $mQ$ (modularity introduced in ~\cite{medical_paper}), it changes gracefully while varying coupling link
% density of the multilayer network (see Fig.~\ref{single}).
We have demonstrated the utility of $Q_M$ by developing multilayer community detection 
algorithms \textbf{GN-$Q_M$} and \textbf{Louvain-$Q_M$}, substituting vanilla modularity by $Q_M$ in classical community detection 
techniques. We have proved the convergence of both the proposed algorithms along with the complexity analysis.
% This observation essentially enables us to re-use the rich literature available for single layer community detection algorithms and merge
% $Q_M$ with any such standard algorithm.
% In this work, we have chosen to show our results with Louvain~\cite{blondel2008fast} and Girvan-Newman~\cite{newman2004fast} community
% detection algorithms.
%Notably, our approach is free from any external parameters.
% Our approach directly inherits the following advantages of the chosen algorithms
% (a) it is free from external parameters (say, number of communities);
% (b) it is fast and scalable to large-scale networks.
In order to examine the modularity $Q_M$ and evaluate the proposed algorithms in a controlled environment, we have developed a 
methodology to generate multilayer synthetic networks with pre-planted communities.
Our algorithms perform observably better than state-of-the-art community detection techniques for wide
spectrum of network parameters. Especially, unlike the competing algorithms, their performance remain almost invariant with
respect to the fraction of cross layer vs single layer communities present in the network. Finally, communities discovered 
by our algorithms exhibit practical applications for recommending locations in Yelp as well as recommending groups in Meetup, reflecting 
the effectiveness of our approach on
empirical dataset.
%May mention a disadvantage that we cannot expand it for hyperedges because corresponding k-partite modularity does not exist.
%\vspace{-0.05in} 